Throughout this report, we have demonstrated a collection of enhancements that
could be made to the user interface of a typical Unix command line shell. We
strongly believe that these, or similar, enhancements have a great potential to
increase the efficiency, usability, and understand-ability of command line
interfaces. The web-based prototype we developed for our system allowed us to
test out our ideas, and our initial user study can help us see what to focus on
in any future work.

The preferred target audience for our application would be beginners learning to
use Unix for the first time. By targeting those learning the Unix environment
for the first time, we hoped to demonstrate that an improved user interface
design could lead to a better teaching tool. Once we have left the prototype
phase, a more extensive analysis can be carried out, as described in Section
\ref{sec:eval}.

Thus far we have designed a basic web-based prototype of the system, one that
highlights it's novel GUI techniques and core functionality. As is discussed
above, we've gone through a preliminary user study of our prototype. This study
consisted of an entry survey to gauge users' prior experience with the shell,
and attitudes towards the shell. Following a walkthrough of the prototype, we
queried users on their experience: whether they found it usable, educational,
and enjoyable. These results can now be used to evaluate and refine the
prototype in response to users' critiques.

In Section \ref{sec:results} we analyzed the user responses to both surveys. This
section of testing was intended to test the hypothesis that users who use our
program would report a more positive user experience. On the entry survey
querying a user's self-reported experience with the shell with regards to
usability, efficiency, and knowledge users reported an average rating of 1.9,
2.2, and 2.0 respectively (from 1 to 4 in a Likert-style questionnaire). On the
exit survey users ranked the prototype a 1.9, 1.7, and 1.9 on its usability,
educational potential, and their experience with it respectively.

Based upon these ratings, we conclude that our hypothesis here is not supported
by the reactions to this prototype. The command line interface certainly can be
made more user friendly by the application of user interface design techniques,
and more work and research on our prototype can help us accomplish that goal in
the future.

% \emph{THE END}

% From the responses we can speculate a bit as to why, and how we can improve
% future versions of the application.

% * users did not find the design compelling
% * users found the interface confusing
% * users %...

% 9a. Briefly describe what the system is and how you evaluate the system
% 9b. Use a list to describe which hypotheses in Section 7 are supported in the evaluation
% 9c. (optional) List the findings which are in the hyphteses.
% 9d. (optional) List possible strategies to enhanced the system .
%%% Local Variables:
%%% mode: latex
%%% TeX-master: "documentation"
%%% End:
