\subsection{User Stories}
\emph{As a beginner, }
\begin{itemize}
  \item I want to compile my source code.
  \item I want to navigate to my source code.
  \item I want to be able to edit my source.
  \item I want easy access to information about what I am doing.
  \item I want to install the tools I need to make code.
  \item I want to know what I can do.
  \item I want to be able to open everything like I was able in windows.
  \item I want to know what my command is going to do.
  \item I want the same visual feedback a file browser gives me.
  \item I want to know how to utilize my shell’s history.
  \item I want to be able to easily and obviously perform common tasks.
  \item when I type a filename, I want the most common task associate with that file to be suggested.
  \item when I drag a file into the command line, I want that file name to be typed.
\end{itemize}

\emph{As a moderate user, }
\begin{itemize}
  \item I want to automate my workflow.
  \item I want the system to alert me when automation is an option.
\end{itemize}

\emph{As an expert user, }
\begin{itemize}
  \item I want tab-completion that is file-type aware
  \item I want heads up information about my system as I use it
\end{itemize}

\emph{As any user, }
\begin{itemize}
  \item I want to be able to copy and paste.
  \item I want to be able to drag a link into my shell and have the file be
    added to the current directory.
  \item I want the system to learn about my most common tasks.
  \item I want to know what options are available to me for a given command.
  \item I want contextual information displayed to me when composing commands.
  \item I want to view files in the current directory as I move through the
    system.
  \item I want to be able to undo what I've done.
\end{itemize}

\subsection{Hierarchical Analysis of Selected Tasks}
\begin{enumerate}
  \item As any user, I want to be able to undo what I've done.
  \begin{enumerate}
    \item Run a command
    \begin{enumerate}
      \item Know what command to run
      \item Write the command
    \end{enumerate}
    \begin{enumerate}
      \item Understand the results of the command
      \begin{enumerate}
        \item View what files/directories/settings were changed
        \item View how they were changed
      \end{enumerate}
    \end{enumerate}
    \item Undo a command
  \end{enumerate}

  \item As a beginner, I want to know what I can do with a file.
  \begin{enumerate}
    \item Specify a file
    \begin{enumerate}
      \item See what files are in my current working directory
      \item Select one of those files
    \end{enumerate}
    \item View the available commands
    \begin{enumerate}
      \item View a list of what commands would be useful for that file
      \item View what each command does
    \end{enumerate}
    \item Run a command on the file
    \begin{enumerate}
      \item Select a command
    \end{enumerate}
  \end{enumerate}

  \item As a casual user, I want to automate my workflow.
  \begin{enumerate}
    \item Specify a task which needs to be run many times
    \item View suggestions on how to run that task
    \item Select an automation technique
  \end{enumerate}

  \item As a beginner, I want to know what the command is going to do.
  \begin{enumerate}
    \item Specify a command
    \item View that command’s effects
    \begin{enumerate}
      \item View which files are going to be affected
      \item View how those files are going to be affected
    \end{enumerate}
    \item Chose whether to run the command or not
  \end{enumerate}

  \item As an expert user, I want heads-up information about my system as I use it.
  \begin{enumerate}
    \item See what the state of my session is
    \begin{enumerate}
      \item View background jobs
      \item View possible commands based on the current context
      \begin{enumerate}
        \item Take local files into account
      \end{enumerate}
      \item View the ways the current session has been altered - non-normal
      environment variables, virtual environments, et cetera.
    \end{enumerate}
  \end{enumerate}
\end{enumerate}
%%% Local Variables:
%%% mode: latex
%%% TeX-master: t
%%% End:
